Yield and production bias/accuracy

### 2016-12-06 Rmd/c2-landcover-preprocess-2.Rmd
Revisions through 6/12/2016: 1. Manuscript into methods 2. Recompiled library, dealing with bug in raster::mask (masked out by different library) 3. Revised c6-carbon, c8-yield-production to save yield and carbon grids. 4. Created c10-location-impact.Rmd, new analysis to estimate difference in location due to landcover error in yield and carbon stocks

# sum these also with and without horticulture
sumfun <- function(x) sum(x, na.rm = TRUE)
gti <- lapply(list(cover2007, cover2011), function(y) {
  r <- calc(y[[-6]], sumfun)
  r[r > 100] <- 100
  writeRaster(r, file = gsub("\\.tif", "sum.tif", y@file@name), overwrite = TRUE)
})

# Leave commented out in case want to bring back horticulture class
# gti_hort <- lapply(list(cover2007, cover2011), function(y) {
#   r <- calc(y, sumfun)
#   r[r > 100] <- 100
#   writeRaster(r, file = gsub("\\.tif", "sum_h.tif", y@file@name), overwrite = TRUE)
# })

>>>>

# sum these also with and without horticulture
sumfun <- function(x) sum(x, na.rm = TRUE)
# gti <- lapply(list(cover2007, cover2011), function(y) {
#   r <- calc(y[[-6]], sumfun)
#   r[r > 100] <- 100
#   writeRaster(r, file = gsub("\\.tif", "sum.tif", y@file@name), overwrite = TRUE)
# }) 
gti <- lapply(list(cover2007, cover2011), function(y) {
  raster(gsub("\\.tif", "sum.tif", y@file@name))
})

# Leave commented out in case want to bring back horticulture class
gti_hort <- lapply(list(cover2007, cover2011), function(y) {
  r <- calc(y, sumfun)
  r[r > 100] <- 100
  # writeRaster(r, file = gsub("\\.tif", "sum_h.tif", y@file@name), overwrite = TRUE)
  r
})

# calculate areas
cellStats(cover2011[[2]] / 100, sum) / 
  cellStats(calc(cover2011 / 100, sumfun), sum) * 100  # communal areas 18.7\% cropland
cellStats(cover2011[[6]] / 100, sum) / 
  cellStats(calc(cover2011 / 100, sumfun), sum) * 100  # horticulture 3.1\% of cropland

### 2016-12-06 Rmd/c6-carbon.Rmd
Revisions through 6/12/2016: 1. Manuscript into methods 2. Recompiled library, dealing with bug in raster::mask (masked out by different library) 3. Revised c6-carbon, c8-yield-production to save yield and carbon grids. 4. Created c10-location-impact.Rmd, new analysis to estimate difference in location due to landcover error in yield and carbon stocks

## Analysis
### Prepare raster data
```{r, eval=FALSE}
load(full_path(p_data, "d_grid_act.rda"))  # actual diffence grids
paths <- full_path(p_data, dir(p_data, paste0("cover*.*11sum_mask.tif$")))
gti <- raster(paths) / 100  # gti 2011
namask <- raster(full_path(p_data, "namask.tif"))  # NA mask
gti <- mask(gti, namask)  # apply mask to GTI
# cellStats(!is.na(gti), sum)

@@

>>>>

## Analysis
### Prepare raster data
```{r, eval=FALSE}
load(full_path(p_data, "d_grid_act.rda"))  # actual diffence grids
paths <- full_path(p_data, dir(p_data, paste0("cover*.*11sum_mask.tif$")))
gti <- raster(paths) / 100  # gti 2011
namask <- raster(full_path(p_data, "namask.tif"))  # NA mask
gti <- raster::mask(gti, namask)  # apply mask to GTI
# cellStats(!is.na(gti), sum)

@@

# save for further analysis
save(gti_c, lc_c, file = full_path(p_data, "carbon-tier1.rda"))
```
<a href="#top">Back to top</a>

### 2016-12-06 Rmd/c8-yield-production.Rmd
Revisions through 6/12/2016: 1. Manuscript into methods 2. Recompiled library, dealing with bug in raster::mask (masked out by different library) 3. Revised c6-carbon, c8-yield-production to save yield and carbon grids. 4. Created c10-location-impact.Rmd, new analysis to estimate difference in location due to landcover error in yield and carbon stocks

```{r, eval=FALSE}
library(SAcropland)
library(xtable)
library(RColorBrewer)
p_root <- full_path(proj_root("SAcropland"), "SAcropland")
p_fig <- full_path(p_root, "paper/figures/")
p_data <- full_path(p_root, "external/ext_data/")
p_data2 <- full_path(p_root, "data/")
#p_carb <- full_path(p_root, "SAcropland/external/ext_data/carbon/")
# load(full_path(p_data, "yield-bias.rda"))

@@

# check Monfreda's yield data to see how it deals with null areas
monf <- full_path("external/ext_data/monfreda_data/maize_HarvAreaYield_NetCDF",
                  "maize_AreaYieldProduction.nc")
monfmz <- brick(monf, level = 2)
plot(crop(monfmz, spTransform(sa.shp, monfmz@crs)), col = bpy.colors(20))
plot(crop(monfmz, spTransform(sa.shp, monfmz@crs)) > 0)  # almost all SA > 0

@@

DT <- na.omit(as.data.table.raster(s, xy = TRUE))
DT[, wgt := ref * awgts]  # calculate weights from ref and area weights

@@

(Supplmentary analysis not presented). Using yield gap estimates as an indicator. First we'll bring in mean rainfall as a means of calculating a spatial correlation in yield gap estimates. Using data from the Princeton Global Forcing dataset, downloaded from the Africa Flood and Drought Monitor. Note: currently this is only explored here. 
```{r, eval=FALSE}
# rainfall layer prepared for SA crop subsidy analysis
load("external/ext_data/climate/mag_dist_clim.rda")
pre <- calc(pre2, mean)  # 31 year mean rainfall for Africa
p4s <- projection(raster(nrow = 10, ncol = 10)) # GCS
presa <- crop(pre, spTransform(sa.shp, p4s))  # crop to SA
projection(presa) <- p4s  
presa <- projectRaster(presa, lcu$f25$sa30)  # project to Albers
presa <- mask(presa, awgts$f25, maskvalue = 0)  # mask
presa1k <- disaggregate(presa, fact = 25)

@@

save(list = ls(), file = full_path(p_data, "yield-bias.rda"))
```
<a href="#top">Back to top</a>

>>>>

```{r, eval=FALSE}
library(SAcropland)
library(xtable)
library(RColorBrewer)
library(spatstat)
p_root <- full_path(proj_root("SAcropland"), "SAcropland")
p_fig <- full_path(p_root, "paper/figures/")
p_data <- full_path(p_root, "external/ext_data/")
p_data2 <- full_path(p_root, "data/")
#p_carb <- full_path(p_root, "SAcropland/external/ext_data/carbon/")
# load(full_path(p_data, "yield-bias.rda"))

@@

# check Monfreda's yield data to see how it deals with null areas
monf <- full_path("external/ext_data/monfreda_data/maize_HarvAreaYield_NetCDF",
                  "maize_AreaYieldProduction.nc")
# monfmz <- brick(monf, level = 2, varname = "maizeData")
monfmz <- raster(monf, level = 2)

plot(crop(monfmz, spTransform(sa.shp, monfmz@crs)), col = bpy.colors(20))
plot(crop(monfmz, spTransform(sa.shp, monfmz@crs)) > 0)  # almost all SA > 0

@@

# DT <- na.omit(as.data.table.raster(s, xy = TRUE))
# DT[, wgt := ref * awgts]  # calculate weights from ref and area weights

@@

(Supplmentary analysis not presented). Using yield gap estimates as an indicator. First we'll bring in mean rainfall as a means of calculating a spatial correlation in yield gap estimates. Using data from the Princeton Global Forcing dataset, downloaded from the Africa Flood and Drought Monitor. Note: currently this is only explored here. 
```{r, eval=FALSE}
# rainfall layer prepared for SA crop subsidy analysis
load("external/ext_data/climate/mag_dist_clim.rda")
pre <- calc(pre2, mean)  # 31 year mean rainfall for Africa
p4s <- projection(raster(nrow = 10, ncol = 10)) # GCS
presa <- crop(pre, spTransform(sa.shp, p4s))  # crop to SA
projection(presa) <- p4s  
presa <- projectRaster(presa, lcu$f25$sa30)  # project to Albers
presa <- raster::mask(presa, awgts$f25, maskvalue = 0)  # mask
presa1k <- disaggregate(presa, fact = 25)

@@

save(list = ls(), file = full_path(p_data, "yield-bias.rda"))
save(cyld_agg, cpagg1, file = full_path(p_data, "yieldprod-1km.rda"))
